Manuscript 1 code

### 2024-09-12 manuscript_1_code.Rmd
Changed figure 4c to synchrony stability instead of richness synchrony

```{r richness synchrony mod}
rich_synch_mod <- glmmTMB(synchrony_trans ~ richness_mean*habitat + (1|site), family = beta_family(), data = diversity_stability_synchrony)
summary(rich_synch_mod)
hist(residuals(rich_synch_mod)) # looks good
plot(residuals(rich_synch_mod) ~ fitted(rich_synch_mod)) # same issue as always
r.squaredGLMM(rich_synch_mod) # 0.701, 0.775
emtrends(rich_synch_mod, pairwise ~ habitat, var = "richness_mean") # forereefs aren't different
```

@@

rich_synch_emm <- emmip(rich_synch_mod,
                        habitat ~ richness_mean,
                        at = list(richness_mean = seq(0,10,0.01)), plotit = F, CIs = T)

filtered_rich_synch_effects <- rich_synch_emm %>%
  left_join(dss_ranges, by = c("habitat")) %>%
  filter(richness_mean >= min_richness & richness_mean <= max_richness)

@@

```{r figure 4c}
(figure_4c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = richness_mean, y = synchrony_trans, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_synch_effects, aes(x = richness_mean, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_rich_synch_effects, aes(x = richness_mean, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Synchrony\n", x = "Macroalgal Richness") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
ggsave(filename = "output/figure_4c.png", figure_4c, height = 10, width = 14)
```

>>>>

```{r richness synchrony mod}
synch_stab_mod <- glmmTMB(cover_stability ~ synchrony*habitat + (1|site), family = Gamma("log"), data = diversity_stability_synchrony)
summary(synch_stab_mod)
hist(residuals(synch_stab_mod)) # looks good
plot(residuals(synch_stab_mod) ~ fitted(synch_stab_mod)) # same issue as always
r.squaredGLMM(synch_stab_mod) # 0.63, 0.71
emtrends(synch_stab_mod, pairwise ~ habitat, var = "synchrony") # fringing and backreef not different
```

@@

synch_stab_emm <- emmip(synch_stab_mod,
                        habitat ~ synchrony,
                        at = list(synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_synch_stab_effects <- synch_stab_emm %>%
  left_join(dss_ranges, by = c("habitat")) %>%
  filter(synchrony >= min_synchrony & synchrony <= max_synchrony)

@@

```{r figure 4c}
(figure_4c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_stab_effects, aes(x = synchrony, y = exp(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_synch_stab_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "Synchrony", y = "Stability\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
ggsave(filename = "output/figure_4c.png", figure_4c, height = 10, width = 14)
```
